---
title: "W_UP_01"
author: "Tattiana Rinkenberger"
date: "06/03/2021"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(mydata,aes(x=position,y=pushups))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The boxplot shows that the skill players can do more push-ups than the line players. The boxplot for the skill players showed that 25th percentile were higher than the boxplot of the line players 75th percentile. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```
Variable results showed that the average number of pushups done by a line player is around 17 and the average number done by a skill player is around 50. 

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

The p-value is too low which means that we reject the null hypothesis. There is a difference when it comes to the amount of pushups that both the line and skill players could do. The skill players on average could do 3 times the amount of pushups compared to the line players. 

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We began the assignment with doing a variable analysis which led to looking at the variables given in order to help identify what helper file was needed. After looking at the variables we needed the numerical~cat file which helped us with the problem. After analyzing the numerical~cat helper file we were able to past the commands after changing the variables within each command. After analyzing the results and data I concluded that I rejected the null hypothesis which means that there is a great difference between the amount of pushups that a skill player can do comepared to a line player.